Appunti di Matematica

### 2022-11-29 Secondo Anno/Analisi Matematica 2/mat.tex
aggiornamento sistematico

\printindex
\end{document}

>>>>

    \displaystyle\sum_{n=1}^\infty (-1)^n\frac{1}{n} & a_n=\frac{1}{n}
  \begin{enumerate}
  \item $a_n$ è decrescente?
  \item $\lim\limits_{n\to\infty} a_n=0$?
  \end{enumerate}
    \text{La serie converge } \begin{cases}
                                \frac{1}{n}\geq \frac{1}{n+1} \Rightarrow n+1\geq n
                                & \text{vero}\\
                                \lim\limits_{n\to\infty} \frac{1}{n}=0 & \text{vero}
\subsection{Successioni di funzioni}
$f_n(x)=(f_1(x),f_2(x),\dots,f_n(x),f_{n+1}(x),\dots)$ {\color{red}successione di
  funzioni}
    f_n(x)=x^n(x,x^2\dots x^n)
Si definsce \textit{\color{red}limite} $\lim\limits_{n\to\infty}f_n(x)$ quella $f(x)$ tale
che $\forall \xi >0$ $\exists \nu_{\xi,x}\in N:\forall n >\nu_{(\xi,x)}$:
  \abs{f_n(x)-f(tx)}<\xi
\begin{description}
\item[$(f_n(x)),x\in I$] si definisce {\color{red}semplicemente convergente} se
    \lim\limits_{n\to \infty}f_n(x)=f(x) & \text{cioè } \forall \xi > 0 \exists
                                           \nu_{(\xi,x)} n\in N\\
    & \abs{f_n(x)-f(x)}<\xi
\item[$(f_n(x)), x\in I$] si definisce {\color{red}assolutamente convergente} se
    \lim\limits_{n\to \infty}\abs{f_n(x)}=f(x)
  \item[$(f_n(x)),x\in T$] si definisce {\color{red}uniformemente convergente} se
\end{description}

\printindex
\end{document}
